---
title: "Lab 01 - Hello R"
author: "Fanyi Zeng"
date: "01/14/22"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1
A data frame with 1846 rows and 3 variables:

dataset: indicates which dataset the data are from

x: x-values

y: y-values

### Exercise 2

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

First let's plot the data in the star dataset!

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes (x=x, y=y))+
  geom_point()
```

Next let's calculate the correlation between x and y in this dataset!

```{r cor-star}
star_data %>%
  summarize(r=cor(x,y))
```

### Exercise 4

Plot the data in the circle dataset.

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter (dataset == "circle")
ggplot(data = circle_data, mapping = aes (x=x, y=y))+
  geom_point()
```

Calculate the correlation between x and y in the circle dataset.

```{r cor-circle}
circle_data %>%
  summarize(r=cor(x,y))
```

### Exercise 5

Finally, let’s plot all datasets at once. In order to do this we will make use of faceting. Facet by the dataset variable, placing the plots in a 3 column grid.

```{r}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
```

And we can use the group_by function to generate all the summary correlation coefficients.

```{r}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```

## Bonus Tips by Yoo Ri

Here are some helpful tips :) 

* filter() is for extracting rows

* group_by() is for grouping datasets by assigned column 
* ungroup() cancels the grouping 

* summarize()  is often used with group_by(). This function can print the output according to the group_by().

* facet_grid(y~x,...) creates a grid with variable y as a row, variable x as a column  
* facet_wrap(x,... ) is useful when there is only one variable
